\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-01 paper.tex
added more info generally

@@

@@

ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour.

@@

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules, the
only external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps~\autocite{leafletjs}. We did not use any framework
for developing frontends like Facebook's React or Google's Angular. Instead, all
of the complex UI interactions were handled by modifying the DOM directly with
JavaScript's built-in functionality. Furthermore, we did not use any advanced
frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
of this scope, this was the correct decision. Considering we had limited
knowledge of React or Angular, it was also faster to develop the UI in the
way we were used to from previous experience. But if we were to continue to
develop Editour, UI libraries and frontend build tools would be something to
consider. With these changing requirements, the Editour was becoming onerous to
maintain at this stage of the project. Luckily, these changes were still
manageable to implement.

@@

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. Git and GitHub enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

% TODO give this paragraph some more context so it doens't seem out of place
The way we incorporated branches into our workflow helped us collaborate in a
way that kept us organized. In general, if one of us was working on a specific
feature, we would create a branch with a name descriptive of that feature. This
methodology minimized difficult-to-resolve merge conflicts.
% TODO explain merge conflicts and cite that Atlassian thing

>>>>

All of Unity's scripting is done with C\#, which is a general purpose,
object-oriented language~\autocite{ecmainternational2017}. Even though none of
us had extensive experience with C\# prior to this project, this was not a great
concern since C\# is similar to other object-oriented languages such as Java and
C++. The design goals of the language were also appealing to us; C\# includes
features important for programmer productivity such as strong type checking
(unlike JavaScript), detection of using uninitialized variables (also unlike
JavaScript,) range checking for array bounds (unlike C) and garbage collection.
At the same time, our lack of familiarity with the language and Unity as a whole
is another reason we first looked into cross-platform AR solutions that did not
use Unity.
%TODO see if we need more sources for this

@@

\subsubsection{Editour Frontend Implementation}
\label{sec:editourFrontendImplementation}

The frontend was implemented as a web app, using web technologies such as HTML,
CSS and JavaScript, with JavaScript being the vast majority. ECMAScript is the
standard that modern JavaScript follows.

Type-checking provided by Visual Studio Code and JSDoc made the growing code
complexity more manageable~\footnote{One helpful specification of the ECMAScript
standard in the way of programmer sanity is ``strict mode.'' By placing the
string \texttt{"use strict"} at the top of a JavaScript source file, errors will
be thrown in many cases where ordinary JavaScript would not complain. The
simplest example of this is the line \texttt{a = 1;} will not throw an error
ordinarily. In strict mode, you must at first explicitly declare the variable
with the \texttt{let}, \texttt{var} or \texttt{const} keyword before assigning
it, similar to Java or C++. We included the string at the beginning of every
source file except for class declarations, which are in strict mode by
default~\autocite[386]{ecmainternational2019}.} . Excluding Node.js modules, the
only external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps~\autocite{leafletjs}. We did not use any framework
for developing frontends like Facebook's React or Google's Angular. Instead, all
of the complex UI interactions were handled by modifying the DOM directly with
JavaScript's built-in functionality. Furthermore, we did not use any advanced
frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
of this scope, this was the correct decision. Considering we had limited
knowledge of React or Angular, it was also faster to develop the UI in the way
we were used to from previous experience. But if we were to continue to develop
Editour, UI libraries and frontend build tools would be something to consider.

@@

ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour. The app was built with Unity, which enabled to us
to use a single codebase for the iOS and Android versions of the apps.

@@

At this point in the project, the codebase for Editour was already around three
thousand lines of vanilla JavaScript. With the changing requirements, Editour
was becoming onerous to maintain at this stage of the project. Luckily, these
changes were still manageable to implement.

@@

@@

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. GitHub and git enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

% TODO give this paragraph some more context so it doens't seem out of place
The way we incorporated branches into our workflow helped us collaborate in a
way that kept us organized. In general, if one of us was working on a specific
feature, we would create a branch with a name descriptive of that feature. This
methodology minimized difficult-to-resolve merge conflicts. We modeled this
workflow off of the ``Git Feature Branch Workflow'' Atlassian
tutorial~\autocite{atlassian}.
% TODO explain merge conflicts and cite that Atlassian thing
